|

### 2021-09-10 appendix/appendix.Rmd
final version

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

>>>>

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Danilo Freire[^danilo]"
- "Umberto Mignozzetti[^umberto]"
- "Catarina Roman[^catarina]"
- "Huzeyfe Alptekin[^huzeyfe]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfeire@lincoln.ac.uk>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^catarina]: PhD Student, University of California, San Diego, <acroman@ucsd.edu>, <http://catarinaroman.github.io>.

[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.

### 2021-09-10 article/article.Rmd
final version

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
date: \today
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\". Based on a sample of 30 articles, we find no robust evidence suggesting that legislature size has either a positive or a negative effect on government budgets. Yet the aggregate results mask considerable heterogeneity. Our findings provide moderate support for the \"law of $1/n$\" in unicameral legislatures and in upper houses, but they also indicate that papers using panel/fixed-effects models or regression discontinuity designs report negative public spending estimates. We find only limited evidence that electoral systems impact public spending, which suggests that proportional representation systems may not be more prone to overspending than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

>>>>

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
author:
- "Danilo Freire[^danilo]"
- "Umberto Mignozzetti[^umberto]"
- "Catarina Roman[^catarina]"
- "Huzeyfe Alptekin[^huzeyfe]"
date: \today
thanks: "Freire, Mignozzetti, and Roman contributed equally to all parts of the manuscript. Alptekin helped collect data in the early stages of the project. The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\". Based on a sample of 30 articles, we find no robust evidence suggesting that legislature size has either a positive or a negative effect on government budgets. Yet the aggregate results mask considerable heterogeneity. Our findings provide moderate support for the \"law of $1/n$\" in unicameral legislatures and in upper houses, but they also indicate that papers using panel/fixed-effects models or regression discontinuity designs report negative public spending estimates. We find only limited evidence that electoral systems impact public spending, which suggests that proportional representation systems may not be more prone to overspending than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfeire@lincoln.ac.uk>, <https://danilofreire.github.io>.

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.

[^catarina]: PhD Student, University of California, San Diego, <acroman@ucsd.edu>, <http://catarinaroman.github.io>.

[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
